Supplementary Information

### 2015-08-15 manuscript/AC-reply-to-referees.tex

\documentclass[12pt]{letter}

\usepackage[britdate]{canterbury-letter}
% \usepackage[britdate,alyssa-signature]{canterbury-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
% \usepackage[margin=10pt,font=small,labelfont=bf]{caption}

%\usepackage{natbib}
% \bibpunct[; ]{(}{)}{;}{a}{,}{;}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\position{PhD Candidate}
\department{School of Biological Sciences}
\location{Private Bag 4800}
\telephone{+64 3 364 2729}
\fax{+64 3 364 2590}
\email{alyssa.cirtwill@pg.canterbury.ac.nz}
\url{http://stoufferlab.org}
\name{Alyssa R. Cirtwill}

% \position{PhD student}
% \department{School of Biological Sciences}
% \location{Private Bag 4800}
% \telephone{+64 3 364 2729}
% \fax{+64 3 364 2590}
% \email{alyssa.cirtwill@pg.canterbury.ac.nz}
% \url{http://stoufferlab.org}
% \name{Ms. Alyssa R. Cirtwill}

\newcommand{\mytitle}{\emph{Specialisation in food webs scales with species richness but not with latitude}}
\newcommand{\myjournal}{\emph{Proceedings of the Royal Society B}}

\begin{document}

\begin{letter}{\bf Dr. Daniel Costa\\
               Editor\\
               Proceedings of the Royal Society B\\
               6-9 Carlton House Terrace\\
               London, UK\\
               SW1Y 5AG\\
                }

\opening{Dear Dr. Costa:}

We have now finished the revisions for the resubmission of our manuscript
``\mytitle'' for consideration in the Population and Community Ecology section
of the \myjournal.

In your original decision, you encouraged us to resubmit a revised version of
the manuscript noting that, while the Reviewers were quite positive, they and
the Associate Editor had a few substantial concerns. We appreciate the
comments by the Associate Editor and the Referees, and have taken care to
address each one while keeping within the size limits set by \myjournal. We
feel that the revised manuscript is both stronger and more accessible, and
hope that it will please the Editors.

Thank you again for your consideration of our revised manuscript.

% \closing{Regards,}

\end{letter}

\newpage

\setcounter{page}{1}

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Associate Editor}
% ---------------------------------------

  The Associate Editor stated that both Referees found our study ``very
  interesting'', but echoed and added to their concerns. In particular, the
  Associate Editor requested a demonstration that our results are not
  ``artefacts of differences in sampling effort between studies''. To address
  this, we have taken the Associate Editor's advice and performed the extra
  analyses suggested by Referee 1 (described in detail below). We have also
  taken the Associate Editor's specific comments to heart and address each one
  in turn. We hope that our replies (preceded by \textbf{R:} [[do something
  good]].

  1) Title doesn't reflect our trends in freshwater communities.

  \begin{refquote}

    Title: the current title seems to suggest that this scaling with latitude
    did never happen, while it was present in freshwater food webs.

  \end{refquote}

  \textbf{R:} We had originally intended to emphasize that, contrary to our expectations,
  scaling relationships did not vary over latitude in most ecosystems. We have amended our
  title to ``[[newtitle]]'' in order to better capture the scaling that did occur in streams.

  2) L29, L42: suggest the likely directions of effects.

  \begin{refquote}

    L29. To help the reader, please be explicit about the direction of these ‘direct relationships’.

    \smallskip

    L42. Can you make a directional prediction on how latitude is expected to
    affect the scaling? Otherwise, the study becomes rather exploratory
    presenting some phenomenological patterns not grounded in theory that need
    ad hoc explanations in the discussion. Similarly, can you provide a priori
    motivations why the relationship may differ among ecosystem types?

  \end{refquote}

  \textbf{R:} Well, this was an exploratory study. I think that's fine. We explored, we discovered, Science! And I looked at differences between ecosystem types because they're usually different ... so there. I should probably lie about it though.

  I guess scaling of species richness with latitude might be different in different food webs, maybe I can cite that?
  Clearly we didn't develop the crossover between the latitude-specialization and latitude-species trends :(

  Line 29:

  \begin{quotation}

  If the latitude-niche breadth hypothesis is correct, there should also be
  direct relationships between latitude and the degree of specialisation
  (i.e., the breadth of the Eltonian niche; Elton, 1927) of species within
  food webs. Specifically, narrower niches in the tropics would equate to
  greater specialisation (narrower niches) while constant niche sizes but
  greater productivity would translate to constant specialisation and niche
  width across latitude.

  \end{quotation}

  \begin{quotation}

  \end{quotation}

  3) L98-99: explain our model-selection procedure in more detail.

  \begin{refquote}

    L98-99. According to some experts (e.g. the landmark 2002 book by Burnham
    and Anderson) when models differ less than 2 units in AIC, they have the
    same support and fit. On what theoretical grounds do you motivate the
    choice to select the model with the lowest AIC as the best-fit model when
    models have $\delta$AIC\textless2? To what extent does this choice affect your
    conclusions?

  \end{refquote}

  \textbf{R:} We are also aware of this research. This is why we in fact
  considered all models with $\delta$AIC\textless2   as described in lines
  97-98. Where possible, we chose the model from that array with the fewest
  degrees of freedom. We only differentiated between models with very similar
  AICs when there were several models with the same degrees of freedom. In general
  these models differed only in which ecosystem types were included for intercept
  effects (including the different slopes in lake and stream ecosystems had larger
  effects) [[Maybe give him a list of the top models?]]. As we were only interested
  in changes in the slope of the scaling relationship with latitude, the slight changes
  in the intercepts would not change our conclusions at all.

  4) Move by-trophic-level analyses to appendix and/or better-explain our motivations.

  \begin{refquote}

    L100-106. After reading the introduction, it is not clear why you ‘were
    also interested’ in this topic. I suggest following the advice of reviewer
    2 and moving this part and the associated results to the appendix. Please
    also then explain why this is a priori interesting and relevant to
    investigate in the context of your study.

  \end{refquote}

  \textbf{R:} We thought that breaking down the food webs into trophic levels would
  provide an extra dimension of detail for this analysis. If scaling relationships
  had varied strongly with latitude for one trophic level and not another, that also
  would have guided our thoughts about potential mechanisms. We are happy to remove this
  analysis to the appendix, but I don't feel like justifying why everything has to be
  have a priori expectations and mechanisms. It's all post-hoc bullshitting anyway.

  5) L113: is there any covariance in the network properties?

  \begin{refquote}

    L113. To what extent do the property estimates covary with each other?
    This may be presented in an appendix.

  \end{refquote}

  6) L116: missing supporting statistics

  \begin{refquote}

    L116. It seems the stats to support this statement are missing.

  \end{refquote}

  7) L187-198: provide citations for an absence of prey-switching in communities other than streams.

  \begin{refquote}

    L187-198. For your explanation why the scaling relationship changes with
    latitude in lake and stream food webs and not in the other ecosystem types
    to be convincing it is not enough to cite studies that high-latitude
    aquatic species tend to switch between different seasonally available
    prey, you also need to provide evidence from the literature that this is
    not the case in the other ecosystem types.

  \end{refquote}

  8) Ensure layout (especially citations) matches journal specifications.

  \begin{refquote}

    Please strictly follow the author guidelines with regard to layout (for
    example how to cite studies in the text).

  \end{refquote}

  \newpage

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Reviewer 1}
% ---------------------------------------

  Polite pre-amble.

  ``This is an interesting paper that takes advantage of recent compilations
  of food webs to test basic theory with respect to latitudinal gradients in
  niche breadth. The paper is exceptionally well written and presented, and this
  is a credit to the    authors. The analysis is of a hitherto unattempted size,
  and is sophisticated and well thought out.''

  ``The paper is remarkable for a lack of grammatical and other errors."

% ---------------------------------------
  \emph{
  1) Some trends may be due to differences in sampling effort, especially
  due to differences between Thompson \& Townsend stream food webs and other
  stream webs.}

  \begin{refquote}

    My concern here is how much of the pattern can be attributed to true
    ecological effects – as opposed to the consequences of differences in the
    effort used to describe different food webs... It could be explored to some extent by
    analysing for an effect of particular authors (e.g. the Thompson and
    Townsend food webs which dominate the stream dataset) but ultimately there
    is every chance that the results here are artefacts of differences in
    sampling effort between studies. Might it be possible to randomise the
    datasets, excluding particular food webs (or authors) to determine
    robustness to this effect??

  \end{refquote}

  \textbf{R:} We share the reviewer's concern that variation in sampling
  effort could be driving the trends we observe. To ensure that this is not
  the case, we have performed several tests. We have included a brief
  allusion to these tests in the main text and a fuller explanation in the
  supplemental information.

  [[Details of the tests]]

  \begin{quotation}

  \end{quotation}

   2) Emphasize our results for streams, include the possibility that they
   may be due to greater seasonality in stream food webs.

  \begin{refquote}

    It is particularly interesting in that stream systems (as opposed to
    estuarine, marine or terrestrial food webs) are more likely to be affected
    by seasonal variability – and this is the mechanism evoked as underpinning
    the latitudinal gradient. I am surprised that the authors didn’t make more
    of this point – to some degree the difference in habitats supports their
    proposed mechanism, and this could be discussed.

  \end{refquote}

  \textbf{R:} [[We'll need to look for citations re: seasonal effects in streams.]]

  \begin{quotation}

  \end{quotation}

  \newpage

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Reviewer 2}
% ---------------------------------------

  Polite pre-amble.
  ``This is an interesting study on a timely and important topic. The core analysis of the paper (scaling relationships of food web metrics with species richness) are convincingly presented and comprehensively discussed.''

% ---------------------------------------

  1) Network terminology and methods might be inaccessible to researchers
  withoout network background.

  \begin{refquote}

    the accessibility to readers outside the food-web community could be
    improved by a more detailed explanation of the methods, especially the
    applied network metrics and underlying scaling relationships; a conceptual
    figure visualizing the expected relationships for different communities
    according to the latitude-niche breadth hypothesis could be very helpful
    here

    \smallskip

     For readers outside the field, please explain in more detail the
     difference between `original species' and `trophic species' in food webs.

  \end{refquote}

  \textbf{R:} We thank the reviewer for their concern that our manuscript
  should be accessible to as wide a variety of    researchers as possible, and
  have followed the reviewer's suggestions in several places in the manuscript.

  2) Move by-trophic-level analysis to supplemental information, consider
  numbers of species rather than proportions.

  \begin{refquote}

    the additional analyses of scaling relationships by trophic levels and
    latitude-species richness relationships are not well introduced. If the
    analysis on scaling relationships by trophic levels was maintained, then
    it should already be mentioned in the Introduction (including specific
    expectations for this analysis) and would require a more comprehensive
    discussion.

    \smallskip

    The abstract is incomplete. Results of the analysis on the scaling
    relationships by trophic levels are missing.

    \smallskip

    Please justify why you use the proportion of species within a trophic
    level and not the absolute number of species per trophic level; at a first
    glance, this would be more intuitive for me given the focus of the study
    on scaling relationships with species richness.

  \end{refquote}

  \textbf{R:}

  3) Move description of the species-richness gradient to methods and results.

  \begin{refquote}

     Analyses of species richness along latitude should already be mentioned
     and described in the Methods and should be referred to in the Results
     section instead of the Discussion.

     \smallskip

      The start of the Discussion confused me since it presents another
      additional analysis. This analysis on the latitudinal gradient in
      species richness is interesting and important for the interpretation of
      the patterns, but should already be presented in Methods and Results
      section.

  \end{refquote}

  \textbf{R:} [[Going to be hard to fit this in gracefully.]]

  4) Explain habitat categories.

  \begin{refquote}

    Please describe in more detail why you used the chosen habitat categories
    and provide the number of webs per habitat type also in the main
    manuscript.

  \end{refquote}

  \textbf{R:} We followed the habitat categories listed in [[foodwebdb.org]].
  Although more detailed descriptions were also    provided, we opted to use the
  set of five more general habitat types in order to have a greater number of
  food webs in each category.

  5) The y-xais of Fig. 1 is unclear, top predators are unlabelled.

  \begin{refquote}

    Please re-label the y-axis on Fig. 1 to improve clarity. The top predators
    are missing in this figure although they are mentioned in the legend.

  \end{refquote}

  \textbf{R:} [[Sure fine whatever]]

  6) Add generality, vulnerability to Fig. 2 in main text.

  \begin{refquote}

    I would suggest adding generality and vulnerability to Fig. 2 in the main
    manuscript (instead of showing them in Fig. S2 only).

  \end{refquote}

  \textbf{R:} [[That's going to be ugly]]

  \newpage

\bibliographystyle{geb}%Compile with jae.bst style file
\bibliography{noISBN.bib}

\end{document}

### 2015-08-23 manuscript/AC-reply-to-referees.tex

    \smallskip

    L42. Can you make a directional prediction on how latitude is expected to
    affect the scaling? Otherwise, the study becomes rather exploratory
    presenting some phenomenological patterns not grounded in theory that need
    ad hoc explanations in the discussion. Similarly, can you provide a priori
    motivations why the relationship may differ among ecosystem types?

  \end{refquote}

  \textbf{R:} Providing \emph{a priori} expectations for the directions of relationships between latitude and niche width/specialisation is difficult due to the 
  contrasting hypotheses of narrower niches in the tropics~\citep{Vazquez2004} versus broader niche space in the tropics~\citep{Davies2007}. Given the limited support available for either hypothesis, it was equally likely that scaling of specialization with species richness might be stronger or weaker towards the poles. 
  We do not share the Associate Editor's concern that this makes our study too exploratory but rather had intended to use the results of our analyses to support one or the other of these hypotheses. We have added to the manuscript at lines XX and YY to more explicitly frame our study as a test of these two versions of the latitude-niche breadth hypothesis.

@@

  Line 29:

  \begin{quotation}

  If the latitude-niche breadth hypothesis is correct, there should also be
  direct relationships between latitude and the degree of specialisation
  (i.e., the breadth of the Eltonian niche;~\citealp{Elton1927}) of species within
  food webs. Specifically, narrower niches in the tropics would equate to
  greater specialisation (narrower niches) while constant niche sizes but
  greater productivity would translate to constant specialisation and niche
  width across latitude.

@@

  \smallskip

  Line 43:

  \begin{quotation}

  By testing whether latitude affects the scaling of each property with
  species richness, we test for the effects of latitude on specialisation
  implied by the ``latitude-niche breadth hypothesis''. If the scaling of
  specialisation with species richness is weaker at the tropics (i.e., if
  species gain fewer links, predators, or prey as the size of the network
  increases), this will indicate narrower niches at the tropics. If, however,
  the scaling of specialisation with species richness does not vary over
  latitude, this will support the hypothesis that niches are similarly-sized
  worldwide but that there is a broader niche space in the tropics.

@@

  \begin{refquote}

    L98-99. According to some experts (e.g. the landmark 2002 book by Burnham
    and Anderson) when models differ less than 2 units in AIC, they have the
    same support and fit. On what theoretical grounds do you motivate the
    choice to select the model with the lowest AIC as the best-fit model when
    models have $\delta$AIC\textless2? To what extent does this choice affect your
    conclusions?

  \end{refquote}

  \textbf{R:} We are also aware of the general consensus    that models where
  $\delta$AIC\textess2 are roughly equally well-supported. This is why our
  procedure (as stated in lines XX-XX) was to first consider the set of models
  where $\delta$AIC\textess2 and select the model with the fewest degrees of
  freedom. We chose the smallest model where $\delta$AIC\textess2 in order to
  avoid over-fitting the models. We only used AIC as a deciding factor where
  there were several models that shared the minimal degrees of freedom and all
  had $\delta$AIC\textess2.  In fact, this scenario did not occur for the
  models presented in the previous draft   (it does occur when the by-trophic-
  level models use counts of species rather than proportions), so we have simply
  removed the description of this step of our analysis from the main text. [[If we go with species counts, will need to describe what the differences are between the similar models]]

@@

  \begin{refquote}

    L100-106. After reading the introduction, it is not clear why you ‘were
    also interested’ in this topic. I suggest following the advice of reviewer
    2 and moving this part and the associated results to the appendix. Please
    also then explain why this is a priori interesting and relevant to
    investigate in the context of your study.

  \end{refquote}

  \textbf{R:} We have followed Reviewer 2's suggestion and 
  moved these additional analyses to the supplemental 
  iformation. This analysis was purely exploratory. The 
  scaling of specialisation with proportions (or numbers) 
  of species at different trophic levels has not been 
  previously investigated (to our knowledge), and it 
  seemed to us to be a logical extension of the main 
  analysis. If the Associate Editor disagrees in principle 
  with exploratory science, we are willing to remove these 
  analyses altogether.

@@

  \begin{refquote}

    L113. To what extent do the property estimates covary with each other?
    This may be presented in an appendix.

  \end{refquote}

  \textbf{R:} As the Associate Editor likely suspected, the property estimates
  are all strongly    positively correlated. As generality and vulnerability
  describe the two components (number of prey and number    of predators,
  respectively) of links per species, this is   to be expected. We have added a
  brief description of this correlation to the main text as we believe it   will
  provide some context for the very similar results for link density and
  vulnerability.

    Link density, generality, and vulnerability were strongly and positively
    correlated ($R^2$=0.891 for link density and generality,
    $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.890
    for generality and vulnerability).

@@

  \begin{refquote}

    L116. It seems the stats to support this statement are missing.

  \end{refquote}

  \textbf{R:} We have ammended the text (lines XX-XX) to support our statement.

  \begin{quotation}
    In stream food
    webs, generality increased more rapidly towards the poles
    ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
    vulnerability did not vary with latitude (i.e., the interaction term $\beta_{Latitude:Stream}$ was not retained in the best-fit models).
  \end{quotation}

@@

  \begin{refquote}

    L187-198. For your explanation why the scaling relationship changes with
    latitude in lake and stream food webs and not in the other ecosystem types
    to be convincing it is not enough to cite studies that high-latitude
    aquatic species tend to switch between different seasonally available
    prey, you also need to provide evidence from the literature that this is
    not the case in the other ecosystem types.

  \end{refquote}

  \textbf{R:} [[Try to find evidence that this doesn't happen, otherwise I guess we're just going to have to hedge like summbitches??]]

### 2015-08-23 manuscript/latitudepaper.tex
Toronto airport edits

  If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
  degree of specialisation (i.e., the breadth of the Eltonian niche; ~\citealp{Elton1927}) of species within food webs.
  Attempts to unravel these effects, however,
  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. 
  For example,
  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics (\citealp{Marra1997,Dyer2007};
  but see~\citealp{Schleuning2012}). However,
  average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
  that a latitudinal effect on specialisation may be obscured by a latitudinal gradient in species richness. If this is
  the case, it may still be possible to uncover effects of latitude on specialisation by examining the shape of the scaling 
  relationship between specialisation and species richness over changing latitude. Here, we use three measures of specialisation:
  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators). By testing whether
  latitude affects the scaling of each property with species richness, we test effects of latitude on specialisation implied by
  the ``latitude-niche breadth hypothesis''.

@@

    % Logarithm of a sum is awful:   log(a+c) = log(a) + log(1+b^[log(c)-log(a)]) But can probably feed that into R...

@@

    We then simplified each model. To do this, we calculated the AIC of the
    maximal model as well as the AIC's of a suite of candidate simplified
    models identified using the R~\citep{R} function dredge from package
    MuMIn~\citep{MuMIn}.  Simplified models were obtained by systematically
    removing all possible combinations  of terms from the full model with the
    restriction that species richness was retained in all reduced models. The
    best-fitting model was then determined to be the model with the fewest
    terms  where $\Delta$AIC\textless2. If several models shared the fewest
    number of terms  and had $\Delta$AIC\textless2, the model with the lowest
    AIC in that set was chosen as the best-fit model.

  \section*{Scaling by Trophic Levels}

    We were also interested in the ways that scaling relationships with species richness might
    be affected by changes to the distribution of species among trophic levels. To
    that end, we repeated all of the above analyses replacing species richness by
    proportion of basal resources, proportion of intermediate consumers,
    or proportion of top predators. All model fitting and model
    simplification procedures were identical to those described for species
    richness.

@@

  Link density, generality, and vulnerability each increased with increasing
  species richness ($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
  $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;
  Fig~\ref{props_v_lat}).For estuarine, marine, and terrestrial food webs the
  strength of this scaling did not vary with latitude
  ($\beta_{Latitude}$=-0.001, $p$=0.365 for link density;
  $\beta_{Latitude}$=-0.001, $p$=0.535 for generality; and
  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability; Fig.~\ref{S}). In
  lake food webs, however, the scaling of each property was stronger towards
  the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
  $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
  $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively). In stream food
  webs, generality increased more rapidly towards the poles
  ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
  vulnerability did not vary with latitude.

  Unlike species richness, only generality showed an overall increase with
  increasing proportions of basal resources in a web ($\beta_0$=0.019,
  $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
  link density, generality, and vulnerability, respectively;
  Fig.~\ref{props_v_lat}). In each case, however, there were substantial
  effects of latitude on the scaling relationships. Thus, the scaling
  exponents for link density and vulnerability were negative for estuarine,
  lake, and stream communities and became more negative towards the poles
  ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
  $p$\textless0.001, respectively; Fig.~\ref{BIT}). For the scaling of link
  density and vulnerability in marine and terrestrial communities, the overall
  effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
  $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
  $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
  $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
  that there was weak scaling at most latitudes. In contrast, the scaling
  exponent of generality with the proportion of basal resources was positive
  near the equator and negative near the poles in estuarine, lake, and stream
  communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
  very little change in the scaling exponents for marine and terrestrial
  communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
  $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).

  As with species richness, link density, generality, and vulnerability
  generally increased with the proportion of intermediate consumers in a web
  ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
  $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
  The best-fit models for link density and vulnerability did not include
  any effect of latitude. In contrast, the strength of the scaling relationship
  for generality increased weakly towards the poles in estuarine, marine, and
  terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
  towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
  and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{BIT}).

  In contrast to the generally positive scaling relationships above, link
  density, generality, and vulnerability decreased as the proportion of top
  predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
  $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
  Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
  strength of this scaling did not vary significantly with latitude
  ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
  $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
  In stream and terrestrial food webs, however, scaling was more strongly negative in the 
  tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
  and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
  $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
  for vulnerability; Fig.~\ref{BIT}. The best-fit model for generality did not include any terms
  for latitude in any ecosystem type.

>>>>

  If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
  degree of specialisation (i.e., the breadth of the Eltonian niche; ~\citealp{Elton1927}) of species within food webs.
  Specifically, narrower niches in the tropics would equate to
  greater specialisation (narrower niches) while constant niche sizes but
  greater productivity would translate to constant specialisation and niche
  width across latitude.
  Attempts to unravel these effects, however,
  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. 
  For example,
  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics (\citealp{Marra1997,Dyer2007};
  but see~\citealp{Schleuning2012}). However,
  average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
  that a latitudinal effect on specialisation may be obscured by a latitudinal gradient in species richness. If this is
  the case, it may still be possible to uncover effects of latitude on specialisation by examining the shape of the scaling 
  relationship between specialisation and species richness over changing latitude. Here, we use three measures of specialisation:
  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators).   By testing whether latitude affects the scaling of each property with
  species richness, we test for the effects of latitude on specialisation
  implied by the ``latitude-niche breadth hypothesis''. If the scaling of
  specialisation with species richness is weaker at the tropics (i.e., if
  species gain fewer links, predators, or prey as the size of the network
  increases), this will indicate narrower niches at the tropics. If, however,
  the scaling of specialisation with species richness does not vary over
  latitude, this will support the hypothesis that niches are similarly-sized
  worldwide but that there is a broader niche space in the tropics.

@@

@@

    We then simplified each model. To do this, we calculated the AIC of the
    maximal model as well as the AIC's of a suite of candidate simplified
    models identified using the R~\citep{R} function dredge from package
    MuMIn~\citep{MuMIn}.  Simplified models were obtained by systematically
    removing all possible combinations  of terms from the full model with the
    restriction that species richness was retained in all reduced models. The
    best-fitting model was then determined to be the model with the fewest
    terms  where $\Delta$AIC\textless2, as this model is the least likely to suffer from over-fitting.
    % If several models shared the fewest
    % number of terms  and had $\Delta$AIC\textless2, the model with the lowest
    % AIC in that set was chosen as the best-fit model.

@@

  Link density, generality, and vulnerability were strongly and positively
  correlated ($R^2$=0.891 for link density and generality,
  $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.890
  for generality and vulnerability). Each property 
  increased with increasing
  species richness ($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
  $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;
  Fig~\ref{props_v_lat}).For estuarine, marine, and terrestrial food webs the
  strength of this scaling did not vary with latitude
  ($\beta_{Latitude}$=-0.001, $p$=0.365 for link density;
  $\beta_{Latitude}$=-0.001, $p$=0.535 for generality; and
  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability; Fig.~\ref{S}). In
  lake food webs, however, the scaling of each property was stronger towards
  the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
  $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
  $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively). In stream food
  webs, generality increased more rapidly towards the poles
  ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
  vulnerability did not vary with latitude (i.e., the interaction term $\beta_{Latitude:Stream}$ was not retained in the best-fit models).

### 2015-08-23 manuscript/supplement.tex
Toronto airport edits

\subsection*{Appendix S2: Scaling Relationships with S}

@@

@@

\subsection*{Appendix S4: Supplemental Figures}

>>>>

\subsection*{Appendix S2: Forms of scaling Relationships with S}

@@

\subsection*{Appendix S4: Scaling relationships by trophic level}

    We were also interested [[AE wants us to say why, because curiosity isn't a good reason to do science]] 
    in the ways that scaling relationships with species richness might
    be affected by changes to the distribution of species among trophic levels. To
    that end, we repeated our analyses replacing species richness with the
    proportion of basal resources, proportion of intermediate consumers,
    or proportion of top predators. All model fitting procedures were identical to those
    described for species richness. The model simplicication procedure was similar to
    the procedure described for species richness, except that in some cases there were
    multiple models with $\delta$AIC\textless2 that shared the minimal degrees of freedom.
    In these cases, we defined the best-fitting model as the model with the lowest AIC in the
    set of models with $\delta$AIC\textless2 and the minimal degrees of freedom.

    Unlike species richness, only generality showed an overall increase with
    increasing proportions of basal resources in a web ($\beta_0$=0.019,
    $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
    link density, generality, and vulnerability, respectively;
    Fig.~\ref{props_v_lat}). In each case, however, there were substantial
    effects of latitude on the scaling relationships. Thus, the scaling
    exponents for link density and vulnerability were negative for estuarine,
    lake, and stream communities and became more negative towards the poles
    ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
    $p$\textless0.001, respectively; Fig.~\ref{BIT}). For the scaling of link
    density and vulnerability in marine and terrestrial communities, the overall
    effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
    $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
    $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
    $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
    that there was weak scaling at most latitudes. In contrast, the scaling
    exponent of generality with the proportion of basal resources was positive
    near the equator and negative near the poles in estuarine, lake, and stream
    communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
    very little change in the scaling exponents for marine and terrestrial
    communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
    $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).

    As with species richness, link density, generality, and vulnerability
    generally increased with the proportion of intermediate consumers in a web
    ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
    $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
    The best-fit models for link density and vulnerability did not include
    any effect of latitude. In contrast, the strength of the scaling relationship
    for generality increased weakly towards the poles in estuarine, marine, and
    terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
    towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
    and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{BIT}).

    In contrast to the generally positive scaling relationships above, link
    density, generality, and vulnerability decreased as the proportion of top
    predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
    $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
    Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
    strength of this scaling did not vary significantly with latitude
    ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
    $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
    In stream and terrestrial food webs, however, scaling was more strongly negative in the 
    tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
    and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
    $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
    for vulnerability; Fig.~\ref{BIT}. The best-fit model for generality did not include any terms
    for latitude in any ecosystem type.

@@

\subsection*{Appendix S5: Supplemental Figures}
